\textbf{ Analytic Light Curves in Reflected Light: \\% Phase Curves, Occultations, and Non-Lambertian Scattering for Spherical Planets }

### 2020-05-19 tex/ms.tex
Don't tell the reader how to feel

In the limit that the angular size of the star as seen from the planet is
small, the illumination profile on the surface of the planet will
decrease as the cosine of the angle between the surface normal and the star,
reaching zero at the day/night terminator, an angle $\nicefrac{\pi}{2}$
away from the sub-stellar point. However, if the star is sufficiently large
and the planet is sufficiently close-in, rays originating from near the limb
of the star will reach points on the planet surface beyond this angle.
It is straightforward to show that, provided the stellar radius $R_\star$
is larger than the planet radius $R_p$, the angular extent of the true
day/night terminator past $\nicefrac{\pi}{2}$ is given by
%
\begin{proof}{tau}
    \label{eq:tau}
    \tau &= \arcsin\left( \frac{1 - \nicefrac{R_p}{R_\star}}{\nicefrac{a}{R_\star}} \right)
\end{proof}
%
where $a$ the semi-major axis of the orbit (where we implictly assume
the eccentricity is zero).
For planets like the Earth, this quantity is only about $0.26^\circ$,
resulting in a negligible effect on the planet's light curve. However,
for very close-in planets, the effect can be significant. For instance,
the hot Jupiter Kelt-9b has $\nicefrac{R_p}{R_\star} = 0.083$ and
$\nicefrac{a}{R_\star} = 3.16$
planet \citep{Wong2019}. Assuming zero eccentricity and ignoring any
stellar oblateness
\citep[see][]{Ahlers2020},
the day/night terminator extends $\tau \approx 17^\circ$ past the limb
of that planet. Figure~\ref{fig:extended} shows the illumination profile
of this planet in a Mollweide projection, with the sub-stellar point at
the center, for the point source approximation (left) and accounting for
the finite size of the star (right). In addition to the
displaced day/night terminator, the main difference between
the two profiles is the sub-stellar intensity, which is significantly higher
in the extended source case. This is due to the simple fact that in the point
source case the illumination source is placed at the center of the star,
which is one stellar radius farther from the planet than the point closest
to the planet (the sub-planetary point) in the extended source case.
Once accounting for this difference, the fractional change in the intensity
on the planet away from the sub-stellar point is similar in both cases,
and the intensity anywhere beyond $\nicefrac{\pi}{2}$ is less than one-tenth
the peak value.

>>>>

In the limit that the angular size of the star as seen from the planet is
small, the illumination profile on the surface of the planet will
decrease as the cosine of the angle between the surface normal and the star,
reaching zero at the day/night terminator, an angle $\nicefrac{\pi}{2}$
away from the sub-stellar point. However, if the star is sufficiently large
and the planet is sufficiently close-in, rays originating from near the limb
of the star will reach points on the planet surface beyond this angle.
If the stellar radius $R_\star$
is larger than the planet radius $R_p$, the angular extent of the true
day/night terminator past $\nicefrac{\pi}{2}$ is given by
%
\begin{proof}{tau}
    \label{eq:tau}
    \tau &= \arcsin\left( \frac{1 - \nicefrac{R_p}{R_\star}}{\nicefrac{a}{R_\star}} \right)
\end{proof}
%
where $a$ the semi-major axis of the orbit (where we implictly assume
the eccentricity is zero).
For planets like the Earth, this quantity is only about $0.26^\circ$,
resulting in a negligible effect on the planet's light curve. However,
for very close-in planets, the effect can be significant. For instance,
the hot Jupiter Kelt-9b has $\nicefrac{R_p}{R_\star} = 0.083$ and
$\nicefrac{a}{R_\star} = 3.16$
planet \citep{Wong2019}. Assuming zero eccentricity and ignoring any
stellar oblateness
\citep[see][]{Ahlers2020},
the day/night terminator extends $\tau \approx 17^\circ$ past the limb
of that planet. Figure~\ref{fig:extended} shows the illumination profile
of this planet in a Mollweide projection, with the sub-stellar point at
the center, for the point source approximation (left) and accounting for
the finite size of the star (right). In addition to the
displaced day/night terminator, the main difference between
the two profiles is the sub-stellar intensity, which is significantly higher
in the extended source case. This is due to the simple fact that in the point
source case the illumination source is placed at the center of the star,
which is one stellar radius farther from the planet than the point closest
to the planet (the sub-planetary point) in the extended source case.
Once accounting for this difference, the fractional change in the intensity
on the planet away from the sub-stellar point is similar in both cases,
and the intensity anywhere beyond $\nicefrac{\pi}{2}$ is less than one-tenth
the peak value.
